---
title: "Child Abuse in LA County"
author: "Gia Elise Barboza"
date: "March 21, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This document shows how to download, geocode and map data. The data comes from Los Angeles County open data website. The geocoding is done via ArcGis, Python and R integration. The mapping is done in leaflet. This method makes it possible to keep the workflow in R, while deriving the benefits of ArcGis' geocoding capabilities in a Python framework.

```{r cars}
# Create the color palette
pal <- colorFactor(
  palette = c("darkorange3", "darkorange3", "gold"),
  domain = datgeo$USER_CATEG
)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
# Map the data
leaflet(datgeo) %>%
  addProviderTiles(providers$Esri.WorldStreetMap) %>%
  addCircles(popup = ~IN_City, 
             radius = ~200,
             color = ~pal(USER_CATEG),
             fillOpacity = 1, 
             stroke = FALSE) %>%
  addLegend("bottomright", pal = pal, values = ~USER_CATEG,
            opacity = 1)
```


